---
title: "Welcome to CS 344"
subtitle: "AI / Machine Learning<br>Spring 2021"
author: 
  - "Ken Arnold"
date: '2021-02-03'
output:
  xaringan::moon_reader:
    lib_dir: libs
    css: xaringan-themer.css
    nature:
      highlightStyle: github
      highlightLines: true
      countIncrementalSlides: false
---

```{r setup, include=FALSE}
```

```{r xaringan-themer, include=FALSE, warning=FALSE}
library(xaringanthemer)
#style_duo_accent(
#  primary_color = "#1381B0",
#  secondary_color = "#FF961C",
#  inverse_header_color = "#FFFFFF"
#)
```

class: middle

.center[
## Let's do some machine learning!
]

Pick a partner. Decide who will be the *trainer* and who's the *tester*.

**Trainer**:

* Go to <https://teachablemachine.withgoogle.com/train/image>
* Train a simple classifier using your webcam.
  * Ideas: use your hands, your face, some distinctive objects, ...
* Don't worry about making it super accurate.

**Tester**:

* Try out your partner's classifier (without touching the computer or the same objects).
  * Try to find some situations where it works
  * Try to find the most amusing situation where it fails.

---

## What is this course?

This is a course on developing AI systems using machine learning, with a particular emphasis on deep neural networks.

### Objectives

By the end of this course, you will demonstrate growth in your ability to:

-   *Design, implement,* and *analyze* some state-of-the-art types of data-fueled intelligent systems
-   *Design* and *analyze* how these intelligent systems relate with people, individually and collectively, through a Reformed Christian lens.
-   Communicate the above with peers and members of the general public

---

## Approach

* *Very* hands-on
* "Flipped": read and watch lectures at home, hack together in class
  * Watching and/or reading is expected. Make time for it.

---

## Materials

fast.ai book

Successful and famous, for a reason

fastai = layered API on top of PyTorch

Jupyter Notebooks

---

## Why not just learn this on your own?

This course gives you:

* Structure
* Peers
* Freedom to ask stupid questions

---

## Who am I?

---
