---
title: "Welcome to CS 344"
subtitle: "AI / Machine Learning<br>Spring 2023"
author: 
  - "Ken Arnold"
output:
  xaringan::moon_reader:
    lib_dir: libs
    css: xaringan-themer.css
    nature:
      highlightStyle: github
      highlightLines: true
      countIncrementalSlides: false
      ratio: "16:9"
---

```{r setup, include=FALSE}
# remotes::install_github('yihui/xaringan')
#devtools::install_github("gadenbuie/countdown")
library(countdown)
```

```{r xaringan-themer, include=FALSE, warning=FALSE}
library(xaringanthemer)
#style_duo_accent(
#  primary_color = "#1381B0",
#  secondary_color = "#FF961C",
#  inverse_header_color = "#FFFFFF"
#)
```

## My Story

- Cornell
- MIT Media Lab (+humanism)
- Luminoso
- Harvard
  - organizing things
  - writing and predictive text
- "Do justice with tech"?

---

## God *expects* intelligence

- What *general* aspects of living as creatures require us to act intelligently?
- What *specific* commands has God given to his people that require intelligent action?


???

general:

- "be fruitful and multiply": general command
- eating, drinking, avoiding danger, reproducing
  - farming requires long-term planning
  - hunting requires quick and targeted perception and action

specific:

- how are we to perceive others?
- commanded to empathy: love neighbor as self. simulate another's experience.

Psalm 103:

- **v2**: We are to remember: call to mind, recall past episodes of his work for us, individually and jointly, in our own experience or in history. We are to consider what implications these past episodes have for our present situation. And we are to think not just of episodes (like the Exodus) but also of the promises and statements about God (like the giving of the Law and the promises of blessing).
- **v6**: Now we learn some more specifics about God's intelligence. He “works righteousness and justice”. That is, he uses eternal and grand standards of what the right actions and outcomes are, and applies them to a specific circumstance of each specific person. Furthermore, he identifies that certain people are oppressed—he must observe and evaluate the relationships of authority and vulnerability between people.

To understand this, we must act intelligently—we must recall what God did in and through Moses, understood not through direct experience but through reading and hearing the various accounts of these events. We must be able to understand what it means for a person to be “merciful” and “gracious”—descriptions of someone’s character and general pattern of behavior, abstracted from individual incidents. The concepts of mercy and grace themselves require us to understand moral requirements, evaluate ourselves in light of them (to know that we need mercy and grace), and recognize our state of affairs with God as the result of God being “merciful and gracious”.

---

## Objectives

- Dispel any magic about AI
- Bring wisdom to AI use and development
- Get y'all jobs that ChatGPT won't replace
- Sharpen coding skills

---

## Minimal Logistics

Before Wednesday class:

- Skim the Syllabus
- Sign up for Ed
- Fill out survey

Before Friday class:

- Get *Deep Learning for Coders* (or read the notebook version) and read chapter 1
- Watch <https://course.fast.ai/Lessons/lesson1.html> - includes extra material so don't expect mastery.
- Complete the reading quiz on Moodle


---

.center[
## Let's do some machine learning!
]

Pick a partner. Decide who will be the *trainer* and who's the *tester*.

**Trainer** (needs a laptop):

* Go to <https://teachablemachine.withgoogle.com/train/image>
* Train a simple classifier using your webcam. Ideas:
  - which hand are you holding up? happy or sad face? looking left or right? two colors?
* Don't worry about making it super accurate.

**Tester**:

* Try out your partner's classifier (without touching the computer or the same objects).
  * Try to find some situations where it works
  * Try to write a succinct description of what situations cause it to behave unexpectedly.

We'll share descriptions after...

```{r echo=FALSE, results='asis'}
countdown(minutes=15, update_every=15)
```

